\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-21 paper.tex
Fixed typo

Our proposed grammar, in constrast, unambiguously describes the behavior of Script, is easier to reason about the C++ code, and can (hopefully eventually) serve as basis for further analytic work.

>>>>

Our proposed grammar, in constrast, unambiguously describes the behavior of Script, is easier to reason about than the C++ code, and can (hopefully eventually) serve as basis for further analytic work.
